---
title: "Big Exercise"
author: "Original by Greg Wilson (adopted for teaching by Thomas Koentges)"
date: '2024-03-21'
format:
  typst
execute:
  echo: true
editor: 
  markdown: 
    wrap: sentence
---

```{r setup, include=FALSE}
#| label: setup
#| include: false
library(tidyverse)
library(lubridate)
```

The file `toronto-covid-2021-01-04.csv` contains reports of COVID-19 cases in Toronto.
Load this file to create a tibble called `covid`.

```{r}
#| label: read_data
```

Convert the values in the `gender` column to lower case; replace all "unknown" gender entries with `NA`; and then convert the entire column to a factor.
Do not overwrite `covid`, but instead display the result inline.

```{r}
#| label: unknown_as_na
```

Use `covid` to calculate the ratio of the number of patients who are currently hospitalized to the number of patients who have ever been hospitalized.

```{r}
#| label: hospitalized_ratio
```

Use `covid` to create a summary showing the number of confirmed reports per month in 2020.

```{r}
#| label: confirmed_monthly_2020
```

Construct a model showing how well the number of cases reported in one month predicts the number of cases reported in the next month.
(You may find the `lag()` function useful.)

```{r}
#| label: correlation
```

Create a stacked bar chart with the age groups on the X axis showing the fraction of cases of each source.
Facet the plot by gender:

```{r}
#| label: stacked_bar_chart
```

Count the number of days in 2020 in which the number of reported cases was higher than the number reported the day before.

```{r}
#| label: days_with_more_cases
```

Create a new tibble called `history` showing the number of cases per month for each postal code prefix.
You may display the month using its full name (e.g., "September") or as a number (e.g., "09").

```{r}
#| label: cases_per_month
```

Rearrange the table you just created so that it has 13 columns: one called `postal_code_prefix` and one more for each month.
The first value in each row must be a postal code prefix; the other values in that row must be the number of cases in that region and that month, and missing values must be shown as 0 rather than NA.
Again, you may display the month using its full name or as a number.

```{r}
#| label: cases_per_month_wide
```

The file `classification.xlsx` classifies age ranges into four groups.
Read this file to create a tibble called `classification`.

```{r}
#| label: read_classification
```

Use this tibble and the `covid` tibble to create a new tibble with one column containing the age classification, one called `earliest_reported` showing the first date of a report for that age group, and one called `largest_delay` showing the largest difference (in days) between the episode date and the reported date within that age group.

```{r}
#| label: summarize_classified

```
